\bf Title

### 2024-01-17 article/paper_padic_spec.tex
commit by Simone

\newcommand{\R}{\mathbb{R}} % real numbers
\newcommand{\C}{\mathbb{C}} % complex numbers
\newcommand{\N}{\mathbb{N}} % integers
\newcommand{\allmat}{\mathbb{M}} % matrices
\newcommand{\sym}{\mathbb{S}} % matrices symétriques
\newcommand{\PP}{\mathcal{P}}
\newcommand{\Qc}{\mathcal{Q}}
\renewcommand{\span}[1]{{\text{span}(#1)}} % simone's comments
\newcommand{\calL}{\mathcal{L}} % simone's comments

@@

\begin{definition}
  \label{def_polyhedra}
  A \emph{polyhedron} is a subset $P \subset K^n$ of the form
  $$
  P = \{x \in K^n : \val(\ell_1 \oplus \cdots \oplus \ell_d) \geq 0 \text{ and }
  \val(m_1 \oplus \cdots \oplus m_e) = +\infty\},
  $$
  for some $\ell_1,\ldots,\ell_d,m_1,\ldots,m_e \in K[x]_1$, where $\val,\geq$ and $=$ are applied entrywise.
  We always assume without loss of generality that $m_1,\ldots,m_e$ are affinely independent.
\end{definition}

We recall that that the smallest affine space of $K^n$ containing a set $P \subset K^n$ is called its
\emph{affine hull}. The constraint $\val(m_1 \oplus \cdots \oplus m_e) = +\infty$ in \Cref{def_polyhedra}
is equivalent to $m_1(x) = \cdots = m_e(x) = 0$ and since the forms $m_i$ are affinely independent, it
defines the affine hull of $P$. The \emph{dimension} of $P$ is defined as $n-e$ (namely the dimension of
its affine hull).

@@

\begin{definition}[Smith Normal Form]\label{smith_nf}
  Let $M \in \allmat_{m,n}(K)$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
  matrices $P \in \GL_n(\OK)$ and $Q \in \GL_m(\OK)$, such that
  $$
  S := QMP^{-1} = \pi^{a_1} \oplus \pi^{a_2} \oplus \cdots \oplus \pi^{a_r} \oplus {\bf 0}_{\min(m,n)-r}
  $$
  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$.
  The matrix $S$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $\pi^{a_i}$ the
  \emph{invariant factors}.
\end{definition}
\begin{remark}
  The valuation of the first invariant factor of the SNF of a matrix
  $M \in \allmat_{n,n}(K)$ is the minimum of the valuations of the entries of
  $M$. In particular, the SNF of $M \in \allmat_n(\OK)$ has entries in $\OK$.
\end{remark}

@@

\begin{definition}
  We call a matrix $M \in \mathcal{M}_n(K)$ \emph{positive semidefinite} (in symbols $M \succeq 0$)
  if all its eigenvalues have nonnegative valuation in $\overline{K}$.
  We denote by $\mathcal{M}_n^+(K) \subset \mathcal{M}_n(K)$ the set of positive semidefinite matrices.
  The characteristic polynomial of $M$ is denoted $\chi_M$.
\end{definition}

@@

\begin{corollary}\label{cor_caracsdp}
  $\mathcal{M}_n(\OK) \subset \mathcal{M}_n^+(K)$.
\end{corollary}
\begin{proof}
$\OK$ is a ring therefore the characteristic polynomial of matrix whose coefficients are $p$-adic integers have coefficients ins $Pp$ \simone{je comprends pas}. We conclude by \Cref{caracsdp}.
\end{proof}

@@

\begin{definition}
  \label{def_spectrahedra}
  Let $\mathcal{L} = A_0+\span{A_1,\ldots,A_n} \subset \mathcal{M}_n(K)$ be an affine space, for given
  matrices $A_0,A_1,\ldots,A_n$.
  The set $\mathcal{L} \cap \mathcal{M}_n^+(K)$ is called a \emph{spectrahedron} or equivalently
  its canonical preimage in $K^n$:
  $$
  S = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\}.
  $$
\end{definition}

Remark that \Cref{def_spectrahedra} is invariant under intersection: the intersection of two
(canonical preimages of) spectrahedra is a (canonical image of a) spectrahedron.

>>>>

\newcommand{\R}{\mathbb{R}} % real numbers
\newcommand{\C}{\mathbb{C}} % complex numbers
\newcommand{\N}{\mathbb{N}} % integers
\newcommand{\allmat}{\mathbb{M}} % matrices
\newcommand{\sym}{\mathbb{S}} % matrices symétriques
\newcommand{\PP}{\mathcal{P}}
\newcommand{\Qc}{\mathcal{Q}}
\renewcommand{\span}[1]{{\text{span}(#1)}} % simone's comments
\newcommand{\aff}[1]{{\text{aff}(#1)}} % simone's comments
\newcommand{\relint}[1]{{\text{relint}(#1)}} % simone's comments
\newcommand{\calL}{\mathcal{L}} % simone's comments

@@

\begin{definition}
  \label{def_polyhedra}
  A \emph{polyhedron} is a subset $P \subset K^n$ of the form
  $$
  P = \{x \in K^n : \val(\ell_1 \oplus \cdots \oplus \ell_d) \geq 0 \text{ and }
  \val(m_1 \oplus \cdots \oplus m_e) = +\infty\},
  $$
  for some $\ell_1,\ldots,\ell_d,m_1,\ldots,m_e \in K[x]_1$, where $\val,\geq$ and $=$ are applied entrywise.
  We assume without loss of generality that for every $i=1,\ldots,d$ there exists $x \in P$ such that
  $\val(\ell_i(x))<+\infty$.
\end{definition}

We recall that that the smallest affine space of $K^n$ containing a set $S \subset K^n$ is called its
\emph{affine hull} and denoted $\aff{S}$.
The assumption on forms $\ell_i$ in \Cref{def_polyhedra} implies that the constraint
$\val(m_1 \oplus \cdots \oplus m_e) = +\infty$ defines exactly the affine hull of $P$, in other words
$\aff{P} = \{x \in K^n : m_j(x) = 0,
j=1,\ldots,e\}$. The \emph{dimension} of $P$ is defined as the dimension of $\aff{P}$ (for $e=0$,
$\aff{P}=K^n$ and $P$ has dimension $n$).
The \emph{relative interior} of $P$ is defined as $\relint{P} = \{x \in P : \val(\ell_1 \oplus \cdots \oplus \ell_d)
< +\infty\}$.
Remark that \Cref{def_polyhedra} includes the case $d=0$ corresponding to affine spaces, as in the real case.

@@

\begin{definition}[Smith Normal Form]\label{smith_nf} \simone{Je trouve que la SNF devrait être inclue dans les
  préliminaires, car on l'utilise ailleurs, et laisser cette section pour polyèdre+LP}
  Let $M \in \allmat_{m,n}(K)$ be of rank $r$. There exist unique integers $a_1 \leq \cdots \leq a_r$, and
  matrices $P \in \GL_n(\OK)$ and $Q \in \GL_m(\OK)$, such that
  $$
  S := QMP^{-1} = \pi^{a_1} \oplus \pi^{a_2} \oplus \cdots \oplus \pi^{a_r} \oplus {\bf 0}_{\min(m,n)-r}
  $$
  where ${\bf 0}_{\min(m,n)-r}$ is a null square matrix of size $\min(m,n)-r$.
  The matrix $S$ is called the \emph{Smith Normal Form (SNF)} of $M$, and the elements $\pi^{a_i}$ the
  \emph{invariant factors}.
\end{definition}
\begin{remark}
  The valuation of the first invariant factor of the SNF of a matrix
  $M \in \allmat_{n,n}(K)$ is the minimum of the valuations of the entries of
  $M$. In particular, the SNF of $M \in \allmat_n(\OK)$ has entries in $\OK$.
\end{remark}

@@

\begin{definition}
  We call a matrix $M \in \mathcal{M}_n(K)$ \emph{positive semidefinite} (in symbols $M \succeq 0$)
  if all its eigenvalues have nonnegative valuation in an algebraic closure of $K$.
  We denote by $\mathcal{M}_n^+(K) \subset \mathcal{M}_n(K)$ the set of positive semidefinite matrices.
  The characteristic polynomial of $M$ is denoted $\chi_M$.
\end{definition}

@@

\begin{corollary}\label{cor_caracsdp}
  $\mathcal{M}_n(\OK) \subset \mathcal{M}_n^+(K)$.
\end{corollary}
\begin{proof}
$\OK$ is a ring therefore the characteristic polynomial of matrix whose coefficients are $p$-adic integers have coefficients ins $Pp$ \simone{je comprends pas la fin de la phrase}. We conclude by \Cref{caracsdp}.
\end{proof}

@@

\begin{definition}
  \label{def_spectrahedra}
  Let $\mathcal{L} = A_0+\span{A_1,\ldots,A_n} \subset \mathcal{M}_n(K)$ be an affine space, for some
  $A_0,A_1,\ldots,A_n \in \mathcal{M}_n(K)$.
  The set $\mathcal{L} \cap \mathcal{M}_n^+(K)$ or equivalently,
  its canonical preimage in $K^n$:
  $$
  S_A = \{x \in K^n : A_0+x_1A_1+\cdots+x_nA_n \succeq 0\},
  $$
  is called a \emph{spectrahedron}.
\end{definition}

\begin{remark}
  The class of spectrahedra is closed under intersection. Indeed, for affine spaces $\mathcal{L}_1,\mathcal{L}_2$
  one has $(\mathcal{L}_1 \cap \mathcal{M}_n^+(K)) \cap (\mathcal{L}_2 \cap \mathcal{M}_n^+(K)) =
  (\mathcal{L}_1\cap\mathcal{L}_2) \cap \mathcal{M}_n^+(K)$. Now
  assuming $\mathcal{L}_1 = A_0+\span{A_1,\ldots,A_n}$ and $\mathcal{L}_2 = B_0+\span{B_1,\ldots,B_n}$,
  then 
\end{remark}
